Modal Abstractions for Virtualizing Memory Addresses

### 2023-03-03 programlogic.tex
+

    % \pfpointsto{\lvlsum\crt\lfoff}{\lvlbor\lt}\qfracfotsss\ppts \star

@@

  \ulcorner \textsf{aligned } \vaddr \urcorner \star  \\
  \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo)\\
   \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr 
\end{array} \\

\textsf{where   }\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo) \stackrel{\triangle}{=} \\
 \qquad\qquad \nfpointsto{\mask\vaddr\ft\crthree}{\mask\vaddr\tw\crthree}\entryf\qfracfotsss\naddr \star \\ 
 \qquad\qquad  \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qfracfotss\naddr  \star  \\
  \qquad\qquad \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qfracfots\naddr \star \\
  \qquad\qquad \nfpointsto{\mask\vaddr\ft\entrytw}{\mask\vaddr\tw\entrytw}\entryo\qfracfot\naddr 
   \end{array}
\]
\caption{A Strong Virtual Points-to Relation}
\todo[inline]{These fractions aren't quite right (though I see you added the variance between levels), I can walk you through in our meeting tomorrow.}
  \label{fig:strongvirtualpointsto}
\end{figure*}
\end{remark}
%then we reach to a physical page addr (e.g. \textsf{pa}) 
%\[  \paddr\mapsto_{\textsf{a}}\{1\}\vsome \ast \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfrac\naddr \]

@@

One possible approach to is to just abstracting the \textit{valid} page-table walk existence from a each virtual address (e.g. \textsf{va}) to a physical page address, as \textit{per-element} ownership of a logical \textit{page-table-walk-summarization-map}
\[\mathcal{A}\textsf{bsPTableWalk} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  (\mathcal{W}_{64} \; \rightarrow_{\textrm{fin}}\;  (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) ))\]
provided by a fragmentery ghost resrource ownership of $\mathcal{A}\textsf{bsPTableWalk}$.
\begin{remark}[Exchanging Page-Table-Walk-Summarization Mappings (Tokens) with Physical Page-Table-Walk Pointstos ]
$\mathcal{A}\textsf{PTableWalk}$ is a ghost map resource where fragmental-ownership of an individual key-value pair (per-element) can be handled as a resource. We use this mechanism to separate the virtual-to-physical translation from the physical memory involved: virtual points-to assertions can be defined in terms of fragmental ownership (ownership of an element) of these partial ghost map entry assertions , $\sumwalkabs\vaddr\qfrac\paddr$, plus sharing an invariant ($\mathcal{I}$\textsf{ASpace} in Figure \ref{fig:peraspaceinvariant}) that the current installed page table respects all entries of the mapping, $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$. From one another perspective, unmapping pages collects the fragmental map kvpairs, e.g. $\sumwalkabs\vaddr\qfrac\paddr$, from collecting the assertions, and then can remove them from the ghost map and update the page tables. Critically, physical full ownership of the page tables lives, $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$, in the central invariant on the current page table, so some virtual pointsto assertions can refer to memory in those page tables.% This still works with the modality, since that invariant is also semantically a predicate on a page table root.
\end{remark}
Then, our virtual memory addressing would be the fragmental ownership of the abstract page-table-walk mapping with the physical page address mapping as shown in Figure \ref{fig:virtualpointstosharing}. 
\begin{figure*}
\[
\begin{array}{l}
    \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vpage \stackrel{\triangle}{=} 
  \exists \entryo \ldotp 
  \sumwalkabs\vaddr\qfrac\paddr \star 
   \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr
\end{array}
\]
\caption{Virtual-Pointsto for Sharing Pages}
  \label{fig:virtualpointstosharing}
\end{figure*}

\subsection{Address-Space Abstraction}
\label{sec:aspacemodal}
Abstractions we introduce for virtual address spaces are based on the following aspects:
\begin{enumerate}
\item a global address space invariant asserting the authorative ownership of the ghost map, $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$ 
\item for each ghost page-table-walk mapping,  $\sumwalkabs\vaddr\qfrac\paddr$, there exists concrete physical page-table accesses path
  \[\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo)\]
  \item all virtual pointsto assertions happen to be true in a certain address space, i.e. the truth on address virtualization is indexed by CPUs page table register ($\crthree$ for x86-64), and we present modal reasoning principles for updating $\crthree$ (switching from the current address space to another)  
\end{enumerate}
    \subsubsection{Global Per-Address-Space Invariant}
    \label{sec:peraspaceinvariant}
    Virtual points-to assertions would need to be defined in terms of physical points-to assertions and hardware-specific address translation assertions for mapped virtual addresses ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo)$ in Figure \ref{fig:peraspaceinvariant}). For each virtual address \textit{mapped} with a physical page table entry, abstracted with ghost mappings ($\sumwalkabs\vaddr\qfrac\paddr$) in virtul-pointsto relations as shown in Figure \ref{fig:virtualpointstosharing}), there exsits a physical page table walk.  
    \[ \bigast{(\vaddr, \entryo)\in \ptablestore}{\exists\;(\entryf\;,\entrytr\;,\entrytw)\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\vaddr,\entryf,\entrytr,\entrytw,\entryo)} \]
    By separating the virtual-points Overlapping address spaces — both shared data, and shared page tables
which may see updates — can be coordinated with protocols to ensure those updates preserve
address space invariants.
\begin{figure*}
\[
\begin{array}{l}
  \mathcal{I}\textsf{ASpace} \stackrel{\triangle}{=} \lambda \; \crthree \ldotp
  \exists\;\gammaPred \;\ldotp\; \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \star \\
  \bigast{(\vaddr, \entryo)\in \ptablestore}{\exists\;(\entryf\;,\entrytr\;,\entrytw)\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\vaddr,\entryf,\entrytr,\entrytw,\entryo)}
\end{array}
\]
\caption{Global Address-Space Invariant}
  \label{fig:peraspaceinvariant}
\end{figure*}
\subsubsection{Address-Space Modality}
\label{sec:aspacemodalist}
The truth on an address space, exhibits itself as a contingent truth: a location virtualization assertion (a virtual points-to in \ref{fig:virtualpointstosharing}),  happens to valid in the \textit{current world} (in the current address space), and switching address spaces pulls information out of one \textit{world} into the “current view” of memory, and leaves other assertions true relative to the previous address space.

@@

The choice of resource defining the modal context already exhibits itself as a reasoning principle (Figure \ref{fig:modalcontextinvariance}) in which we can intro/eliminate any resource that is not virtual pointsto into/from modal context without dischargin any obligation. We can use this entailment for  \todo[inline,color=red]{Ask Colin}.
  \[
  \begin{array}{l}
\hbox{(\TirNameStyle{ModalContextInvariance})} \qquad
 [r](Q \star \ell \mapsto_{\textsf{p}} \vpage)  \;\vdash [r](Q) \star \ell \mapsto_{\textsf{p}} \vpage 
  \end{array}
  \]
\begin{remark}[The Choice of Modal Context Definition as a Pattern of Verification Context]
  \label{remark:pattern}
  By choosing the contingency and what defines the modal contex, we simply introduce 
  \begin{enumerate}
  \item the pattern of what the essential abstraction (e.g. address spaces) we care about to do verification for is
  \item how a modal context (e.g. a address-space modality $[r]P$), logically, draws the attention to the certain facts in the interest of reasoning (e.g. virtual pointsto relations in the current address-space in Figure \ref{fig:virtualpointstosharing})
  \item and, offloads the burden of individual bookkeeping of these facts (e.g. virtual pointsto relations per address-space) under different context (e.g. virtual pointsto relations in other address-spaces) via utilizing the \textit{summarization} aspect of the contingency it represents (e.g. other virtual pointsto relations are valid under other certain address-space page-table root addresseses).  
  \end{enumerate}
\end{remark}
\paragraph{Interaction}
\label{sec:interaction}
So far, we have just mentioned the structural properties of our modal definition (Remark \ref{remark:pattern}), and what inherent entailments (Rule \hbox{(\TirNameStyle{ModalContextInvariance})}) these properties provide. However, all these structural aspects of using the address-space modality ($[r]P$) considers the fixed index ($r$) of on the truth $P$. From the client's perspective, structural properties of the modal abstraction mainly constitutes the modal frame with summarizing the facts for one another address-space under the address-space modality roughly as it is in the following spec
\[
\{ \crthree \mapsto_{r} r0 \star \textsf{va1} \mapsto_{v} \textsf{v}_1 \star \textsf{va2} \mapsto_{v} \textsf{v}_2 \star \textsf{va3} \mapsto_{v} \textsf{v}_3 \star [r1]\;P \}
\]
where we see the \textit{current address-space} rooted at $r0$ is loaded into the  \textit{current-view} of the memory with its resources ($ \textsf{va1} \mapsto_{v} \textsf{v}_1 \star \textsf{va2} \mapsto_{v} \textsf{v}_2 \star \textsf{va3} \mapsto_{v} \textsf{v}_3$), and framed by the address-space rooted at $r1$ with resources $P$. 
Now, we need to a rule capturing the notion that switching the address spaces by pulling the resources ($P$) out of the one under modality into the \textit{“current view”} of memory, and leaves other assertions true relative to the previous address space (the one rooted at $r0$). To do so, we need to have a proof rule for the instruction (\lstinline|mov_ctl|) updating the $\crthree$.

@@

Readers familiar with dynamic frames~\cite{parkinson2011relationship} might find it useful to notice that a different perspective on this matter is that virtual points-to assertions are self-stable \emph{except} for changes in \lstinline|cr3|, so framing would then naturally require other means of holding \lstinline|cr3| constant (or saving and restoring it).
Virtual points-to assertions could be made self-stable by also giving them partial ownership over \lstinline|cr3| assertions, but this would require explicitly plumbing that ownership from \emph{all} assertions back to any place an address space change might occur; this would seem to be a far graver loss of modularity than this extra quirk in framing discussions.
\todo{inlined, color= red}[STOP HERE, go back fix the stuff discussed with COLIN]
\begin{figure}
\begin{mathpar}
\inferrule[WriteToMemoryFromReg]{
  \{[r_1](P) \ast cr3=r_2 \ast r = r_2 \ast Q\}\overline{is}
}{
  \{P \ast cr3=r_1 \ast r=r_2 \ast [r_2](Q)\}
  \texttt{mov}~\texttt{\%cr3},~r;\;\overline{is}
  %\lstinline|mov %cr3, r| 
} 
\inferrule[WriteToRegFromReg]{
  \{[r_1](P) \ast cr3=r_2 \ast r = r_2 \ast Q\}\overline{is}
}{
  \{P \ast cr3=r_1 \ast r=r_2 \ast [r_2](Q)\}
  \texttt{mov}~\texttt{\%cr3},~r;\;\overline{is}
  %\lstinline|mov %cr3, r| 
} \\ 
\inferrule[WriteToRegFromMem]{
  \{[r_1](P) \ast cr3=r_2 \ast r = r_2 \ast Q\}\overline{is}
}{
  \{P \ast cr3=r_1 \ast r=r_2 \ast [r_2](Q)\}
  \texttt{mov}~\texttt{\%cr3},~r;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\inferrule[WriteToCtlFromReg]{
  \{[r_1](P) \ast cr3=r_2 \ast r = r_2 \ast Q\}\overline{is}
}{
  \{P \ast cr3=r_1 \ast r=r_2 \ast [r_2](Q)\}
  \texttt{mov}~\texttt{\%cr3},~r;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\end{mathpar}
\caption{Selected Reasoning Rules for ..}
\label{fig:wpdamd}
\end{figure}

>>>>

    % \pfpointsto{\lvlsum\crt\lfoff}{\lvlbor\lt}\qfracfotsss\ppts \ast

@@

  \ulcorner \textsf{aligned } \vaddr \urcorner \ast  \\
  \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo)\\
   \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr 
\end{array} \\

\textsf{where   }\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo) \stackrel{\triangle}{=} \\
 \qquad\qquad \nfpointsto{\mask\vaddr\ft\crthree}{\mask\vaddr\tw\crthree}\entryf\qfracfotsss\naddr \ast \\ 
 \qquad\qquad  \nfpointsto{\mask\vaddr\ft\entryf}{\mask\vaddr\tw\entryf}\entrytr\qfracfotss\naddr  \ast  \\
  \qquad\qquad \nfpointsto{\mask\vaddr\ft\entrytr}{\mask\vaddr\tw\entrytr}\entrytw\qfracfots\naddr \ast \\
  \qquad\qquad \nfpointsto{\mask\vaddr\ft\entrytw}{\mask\vaddr\tw\entrytw}\entryo\qfracfot\naddr 
   \end{array}
\]
\caption{A Strong Virtual Points-to Relation}
\todo[inline]{These fractions aren't quite right (though I see you added the variance between levels), I can walk you through in our meeting tomorrow.}
  \label{fig:strongvirtualpointsto}
\end{figure*}
\end{remark}
%then we reach to a physical page addr (e.g. \textsf{pa}) 
%\[  \paddr\mapsto_{\textsf{a}}\{1\}\vsome \ast \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfrac\naddr \]

@@

One possible approach to is to just abstracting the \textit{valid} page-table walk existence from a each virtual address (e.g. \textsf{va}) to a physical page address, as \textit{per-element} ownership of a logical \textit{page-table-walk-summarization-map}
\[\mathcal{A}\textsf{bsPTableWalk} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  (\mathcal{W}_{64} \; \rightarrow_{\textrm{fin}}\;  (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) ))\]
provided by a fragmentery ghost resrource ownership of $\mathcal{A}\textsf{bsPTableWalk}$.
\begin{remark}[Exchanging Page-Table-Walk-Summarization Mappings (Tokens) with Physical Page-Table-Walk Pointstos ]
$\mathcal{A}\textsf{PTableWalk}$ is a ghost map resource where fragmental-ownership of an individual key-value pair (per-element) can be handled as a resource. We use this mechanism to separate the virtual-to-physical translation from the physical memory involved: virtual points-to assertions can be defined in terms of fragmental ownership (ownership of an element) of these partial ghost map entry assertions , $\sumwalkabs\vaddr\qfrac\paddr$, plus sharing an invariant ($\mathcal{I}$\textsf{ASpace} in Figure \ref{fig:peraspaceinvariant}) that the current installed page table respects all entries of the mapping, $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$. From one another perspective, unmapping pages collects the fragmental map kvpairs, e.g. $\sumwalkabs\vaddr\qfrac\paddr$, from collecting the assertions, and then can remove them from the ghost map and update the page tables. Critically, physical full ownership of the page tables lives, $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$, in the central invariant on the current page table, so some virtual pointsto assertions can refer to memory in those page tables.% This still works with the modality, since that invariant is also semantically a predicate on a page table root.
\end{remark}
Then, our virtual memory addressing would be the fragmental ownership of the abstract page-table-walk mapping with the physical page address mapping as shown in Figure \ref{fig:virtualpointstosharing}. 
\begin{figure*}
\[
\begin{array}{l}
    \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vpage \stackrel{\triangle}{=} 
  \exists \entryo \ldotp 
  \sumwalkabs\vaddr\qfrac\paddr \ast 
   \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr
\end{array}
\]
\caption{Virtual-Pointsto for Sharing Pages}
  \label{fig:virtualpointstosharing}
\end{figure*}

\subsection{Address-Space Abstraction}
\label{sec:aspacemodal}
Abstractions we introduce for virtual address spaces are based on the following aspects:
\begin{enumerate}
\item a global address space invariant asserting the authorative ownership of the ghost map, $\ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}}$ 
\item for each ghost page-table-walk mapping,  $\sumwalkabs\vaddr\qfrac\paddr$, there exists concrete physical page-table accesses path
  \[\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo)\]
  \item all virtual pointsto assertions happen to be true in a certain address space, i.e. the truth on address virtualization is indexed by CPUs page table register ($\crthree$ for x86-64), and we present modal reasoning principles for updating $\crthree$ (switching from the current address space to another)  
\end{enumerate}
    \subsubsection{Global Per-Address-Space Invariant}
    \label{sec:peraspaceinvariant}
    Virtual points-to assertions would need to be defined in terms of physical points-to assertions and hardware-specific address translation assertions for mapped virtual addresses ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo)$ in Figure \ref{fig:peraspaceinvariant}). For each virtual address \textit{mapped} with a physical page table entry, abstracted with ghost mappings ($\sumwalkabs\vaddr\qfrac\paddr$) in virtul-pointsto relations as shown in Figure \ref{fig:virtualpointstosharing}), there exsits a physical page table walk.  
    \[ \bigast{(\vaddr, \entryo)\in \ptablestore}{\exists\;(\entryf\;,\entrytr\;,\entrytw)\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\vaddr,\entryf,\entrytr,\entrytw,\entryo)} \]
    By separating the virtual-points Overlapping address spaces — both shared data, and shared page tables
which may see updates — can be coordinated with protocols to ensure those updates preserve
address space invariants.
\begin{figure*}
\[
\begin{array}{l}
  \mathcal{I}\textsf{ASpace} \stackrel{\triangle}{=} \lambda \; \crthree \ldotp
  \exists\;\gammaPred \;\ldotp\; \ownGhost\gammaPred{\authfull{\ptableabswalk\ptablestore}} \ast \\
  \bigast{(\vaddr, \entryo)\in \ptablestore}{\exists\;(\entryf\;,\entrytr\;,\entrytw)\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\vaddr,\entryf,\entrytr,\entrytw,\entryo)}
\end{array}
\]
\caption{Global Address-Space Invariant}
  \label{fig:peraspaceinvariant}
\end{figure*}
\subsubsection{Address-Space Modality}
\label{sec:aspacemodalist}
The truth on an address space, exhibits itself as a contingent truth: a location virtualization assertion (a virtual points-to in \ref{fig:virtualpointstosharing}),  happens to valid in the \textit{current world} (in the current address space), and switching address spaces pulls information out of one \textit{world} into the “current view” of memory, and leaves other assertions true relative to the previous address space.

@@

The choice of resource defining the modal context already exhibits itself as a reasoning principle (Figure \ref{fig:modalcontextinvariance}) in which we can intro/eliminate any resource that is not virtual pointsto into/from modal context without dischargin any obligation. We can use this entailment for  \todo[inline,color=red]{Ask Colin}.
  \[
  \begin{array}{l}
\hbox{(\TirNameStyle{ModalContextInvariance})} \qquad
 [r](Q \ast \ell \mapsto_{\textsf{p}} \vpage)  \;\vdash [r](Q) \ast \ell \mapsto_{\textsf{p}} \vpage 
  \end{array}
  \]
\begin{remark}[The Choice of Modal Context Definition as a Pattern of Verification Context]
  \label{remark:pattern}
  By choosing the contingency and what defines the modal contex, we simply introduce 
  \begin{enumerate}
  \item the pattern of what the essential abstraction (e.g. address spaces) we care about to do verification for is
  \item how a modal context (e.g. a address-space modality $[r]P$), logically, draws the attention to the certain facts in the interest of reasoning (e.g. virtual pointsto relations in the current address-space in Figure \ref{fig:virtualpointstosharing})
  \item and, offloads the burden of individual bookkeeping of these facts (e.g. virtual pointsto relations per address-space) under different context (e.g. virtual pointsto relations in other address-spaces) via utilizing the \textit{summarization} aspect of the contingency it represents (e.g. other virtual pointsto relations are valid under other certain address-space page-table root addresseses).  
  \end{enumerate}
\end{remark}
\paragraph{Interaction}
\label{sec:interaction}
So far, we have just mentioned the structural properties of our modal definition (Remark \ref{remark:pattern}), and what inherent entailments (Rule \hbox{(\TirNameStyle{ModalContextInvariance})}) these properties provide. However, all these structural aspects of using the address-space modality ($[r]P$) considers the fixed index ($r$) of on the truth $P$. From the client's perspective, structural properties of the modal abstraction mainly constitutes the modal frame with summarizing the facts for one another address-space under the address-space modality roughly as it is in the following spec
\[
\{ \crthree \mapsto_{r} r0 \ast \textsf{va1} \mapsto_{v} \textsf{v}_1 \ast \textsf{va2} \mapsto_{v} \textsf{v}_2 \ast \textsf{va3} \mapsto_{v} \textsf{v}_3 \ast [r1]\;P \}
\]
where we see the \textit{current address-space} rooted at $r0$ is loaded into the  \textit{current-view} of the memory with its resources ($ \textsf{va1} \mapsto_{v} \textsf{v}_1 \ast \textsf{va2} \mapsto_{v} \textsf{v}_2 \ast \textsf{va3} \mapsto_{v} \textsf{v}_3$), and framed by the address-space rooted at $r1$ with resources $P$. 
Now, we need to a rule capturing the notion that switching the address spaces by pulling the resources ($P$) out of the one under modality into the \textit{“current view”} of memory, and leaves other assertions true relative to the previous address space (the one rooted at $r0$). To do so, we need to have a proof rule for the instruction (\lstinline|mov_ctl|) updating the $\crthree$.

@@

Readers familiar with dynamic frames~\cite{parkinson2011relationship} might find it useful to notice that a different perspective on this matter is that virtual points-to assertions are self-stable \emph{except} for changes in \lstinline|cr3|, so framing would then naturally require other means of holding \lstinline|cr3| constant (or saving and restoring it).
Virtual points-to assertions could be made self-stable by also giving them partial ownership over \lstinline|cr3| assertions, but this would require explicitly plumbing that ownership from \emph{all} assertions back to any place an address space change might occur; this would seem to be a far graver loss of modularity than this extra quirk in framing discussions.
\begin{figure}
\begin{mathpar}
\inferrule[WriteToRegFromReg]{
  \{P \ast r_d \mapsto_{r} \texttt{rvs} \ast r_s \mapsto_{r}\{q\} \texttt{ rvs} \}\;\overline{ is}
}{
  \{P \ast r_d \mapsto_{r} \texttt{rvd} \ast r_s \mapsto_{r}\{q\} \texttt{ rvs} \}
  \texttt{ mov}~\texttt{r}_d,~\texttt{r}_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\\
\inferrule[WriteToMemFromReg]{
  \{P \ast r_s \mapsto_{r}\{q\}  \texttt{rvs} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \ast r_a \mapsto_{r} \{q\} \texttt{ vaddr} \ast \texttt{vaddr} \mapsto_{t,\texttt{cr3val}} \texttt{v} \}\;\overline{ is}  
}{
  \{P \ast r_s \mapsto_{r}\{q\}  \texttt{rvs} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \ast r_a \mapsto_{r}\{q\} \texttt{ vaddr} \ast \texttt{vaddr} \mapsto_{t,\texttt{cr3val}} \texttt{rvs} \}
  \texttt{ mov}~\texttt{r}_a,~\texttt{r}_s;\;\overline{is}
}
\\
\inferrule[WriteToRegFromMem]{
  \{P \ast r_d \mapsto_{r}  \texttt{v} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \ast r_a \mapsto_{r} \{q\} \texttt{ vaddr} \ast \texttt{vaddr} \mapsto_{t,\texttt{cr3val}} \texttt{v} \}\;\overline{is}
}{
  \{P \ast r_d \mapsto_{r}  \texttt{rvd} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \ast r_a \mapsto_{r} \{q\} \texttt{ vaddr} \ast \texttt{vaddr} \mapsto_{t,\texttt{cr3val}} \texttt{v} \}
  \texttt{mov}~\texttt{r}_d,~\texttt{r}_a;\;\overline{is}
}
\\
\inferrule[WriteToRegCtlFromReg]{
  \{P \ast r_s \mapsto_{r}\{q\}  \texttt{ rvs} \ast \lstinline|cr3| \mapsto_{r} \texttt{rvs}  \}\overline{is}
}{
  \{P \ast r_s \mapsto_{r}\{q\}  \texttt{ rvs} \ast \lstinline|cr3| \mapsto_{r} \texttt{cr3val}  \}
  \texttt{mov}~\texttt{cr3},~r_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\end{mathpar}
\caption{Selected Reasoning Rules for ..}
\label{fig:wpdamd}
\end{figure}
